Corotating Dust Clumps Around Adolescent M-Dwarfs: Four Years of TESS

### 2023-06-25 paper/ms.tex
update ms

\title{Dust Clumps In Corotation Around Adolescent M-Dwarfs: Four Years of TESS}

@@

Given the effective temperatures and stellar radii from the SED fit,
we then estimate the mass by interpolating against the ``magnetic''
models of \citet{2016A&A...593A..99F}.  The need for models that
incorporate some form of magnetic correction is well-documented for
our regime of active, young M-dwarfs
\citep[e.g.][]{2012ApJ...756...47S,2015ApJ...804..146D,2020ApJ...891...29S}.
While one could of course allow a range of magnetic field strengths,
and a corresponding range of fractions for starspot converage
\citep{2020ApJ...891...29S}, we prefer the magnetic
\citet{2016A&A...593A..99F} models based on the simplicity of their
assumption that the surface magnetic field strength will be fixed at
equipartition.
We therefore interpolate our SED-measured temperatures and radii, at
the known cluster-based stellar ages ages, in order to estimate
(model-dependent) stellar masses.
For the two systems without known ages (see below), we omit this mass
estimate, due to the degeneracies in the inference problem.

>>>>

\title{Corotating Dust Clumps Around Adolescent M-Dwarfs: Four Years of TESS}

@@

Given the effective temperatures and stellar radii from the SED fit,
we then estimate the mass by interpolating against the ``magnetic''
models of \citet{2016A&A...593A..99F}.  The need for models that
incorporate some form of magnetic correction is well-documented for
our regime of active, young M-dwarfs
\citep[e.g.][]{2012ApJ...756...47S,2015ApJ...804..146D,2020ApJ...891...29S}.
While one could of course allow a range of magnetic field strengths,
and a corresponding range of fractions for starspot converage
\citep{2020ApJ...891...29S}, we prefer the magnetic
\citet{2016A&A...593A..99F} models based on the simplicity of their
assumption that the surface magnetic field strength will be fixed at
thermal equipartition.
We therefore interpolate our SED-measured temperatures and radii, at
the known cluster-based stellar ages ages, in order to estimate
(model-dependent) stellar masses.
For the two systems without known ages (see below), we omit this mass
estimate, due to the degeneracies in the inference problem.
